Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/appendix.tex

\section{Appendix}
\subsection{Proofs}
Unless stated explicitely, all the propositions consider the Multi-Target linear regression problem.
\begin{proposition}
\label{gps_equivalence}
  $\forall (n, p) \in \mathbb{N}_+^2, \bm{y} \in \mathbb{R}^{n}, \bm{x} \in \mathbb{R}^{p} \lambda \in \mathbb{R}$

@@

\begin{proof}
  We will split this proof in two parts. First we will show that there is at least
  one global minimum, then we will show how to construct $2^n - 1$ other distinct
  solutions with the same objective.
\\ \textbf{Part 1:}
The two components of the expression are always positive so we know that this problem is bounded by below by $0$. $\Omega_{\lambda, \lambda_2, p}^{rs}$ is trivially coercive. Since we have a sum of terms, all bounded by below by $0$ and one of them is coercive, then the entire function admit at least one global minimum.
\\ \textbf{Part 2:} Let's consider one global minimum. For each component $k$ of $\bm{\beta_i}$ for some $i$. Negating it and negating the $k^{th}$ column of $\bm{A_i}$ do not change the the first part of the objetive because the two factors cancel each other. The two norms do not change either because by definition the norm is independant of the sign. As a result these two sets of parameter have the same value and by extension also global minimuma. It is easy to see that going from this global minimum we can decide to negate or not each element in each $\bm{\beta_i}$. We have a binary choice for each parameter, there are $k = \sum_{i=1}^n \#\bm{\beta_i}$ parameters, so we have at least $2^k$ global minima.

\end{proof}
\subsection{Multi-Target Linear and Multi-Class Logistic regressions experiments}
As we showed, Group sparsity share similarities with our method, and we claim
that ShrinkNets are a relaxation of group sparsity.  In this experiment we want
to compare the two aproaches.  We decided to focus on multi-target linear
regression because in the single target case, groups in the Group Sparsity
problem would have a size of one ($\bm{A}$ would be a vector in this case).

@@

For each dataset we fit with different regularization parameters and measure
the error and sparsity obtained after convergence. In this context we define
sparsity as the ratio of columns that have all their weight under $10^{-3}$ in
absolute value. Regularization parameters were choosed in order to obtain the
widest sparsity spectrum. Loss is normalized depending on the problem to be in
the $[0, 1]$ range. We summarized the results in \cref{sparsity_accuracy}. From
our experiments it is clear that ShrinkNets can fit the data closer than Group
Sparsity for the same amount of sparsity. The fact that we are able to reach
very low loss demonstrate that even if our objective function is non convex, in
practice it works as good or better as convex alternatives.
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{regressions}
\vspace*{-5mm}
\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression. From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}

>>>>

%!TEX root=paper.tex
\section{Appendix}

\begin{figure}[t]
\begin{center}
\includegraphics[width=.7\columnwidth]{regressions}
\vspace*{-5mm}
\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression. From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}

\subsection{Proofs}
Unless stated explicitely, all the propositions consider the Multi-Target linear regression problem.
\begin{proposition}
\label{gps_equivalence}
  $\forall (n, p) \in \mathbb{N}_+^2, \bm{y} \in \mathbb{R}^{n}, \bm{x} \in \mathbb{R}^{p} \lambda \in \mathbb{R}$

@@

\begin{proof}
  We will split this proof in two parts. First we will show that there is at least
  one global minimum, then we will show how to construct $2^n - 1$ other distinct
  solutions with the same objective.
\\ \textbf{Part 1:}
The two components of the expression are always positive so we know that this problem is bounded by below by $0$. $\Omega_{\lambda, \lambda_2, p}^{rs}$ is trivially coercive. Since we have a sum of terms, all bounded by below by $0$ and one of them is coercive, then the entire function admit at least one global minimum.
\\ \textbf{Part 2:} Let's consider one global minimum. For each component $k$ of $\bm{\beta_i}$ for some $i$. Negating it and negating the $k^{th}$ column of $\bm{A_i}$ do not change the the first part of the objective because the two factors cancel each other. The two norms do not change either because by definition the norm is independant of the sign. As a result these two sets of parameter have the same value and by extension also global minimuma. It is easy to see that going from this global minimum we can decide to negate or not each element in each $\bm{\beta_i}$. We have a binary choice for each parameter, there are $k = \sum_{i=1}^n \#\bm{\beta_i}$ parameters, so we have at least $2^k$ global minima.

\end{proof}
\subsection{Multi-Target Linear and Multi-Class Logistic regressions experiments}
As we showed, Group sparsity share similarities with our method, and we claim
that ShrinkNets are a relaxation of Group sparsity.  In this experiment we want
to compare the two aproaches.  We decided to focus on multi-target linear
regression because in the single target case, groups in the Group Sparsity
problem would have a size of one ($\bm{A}$ would be a vector in this case).

@@

For each dataset we fit with different regularization parameters and measure
the error and sparsity obtained after convergence. In this context we define
sparsity as the ratio of columns that have all their weights under $10^{-3}$ in
absolute value. Regularization parameters were choosen in order to obtain the
widest sparsity spectrum. Loss is normalized depending on the problem to be in
the $[0, 1]$ range. We summarized the results in \cref{sparsity_accuracy}. From
our experiments it is clear that ShrinkNets can fit the data closer than Group
Sparsity for the same amount of sparsity. The fact that we are able to reach
very low loss demonstrate that even if our objective function is non convex, in
practice it works as good or better as convex alternatives.

### 2018-02-09 paper/ICML/impl.tex

\textbf{Sign change strategy}: Under this strategy neurons are removed when
the weight value changes its sign. This strategy works well in practice but it
is also sensitive to gradient noise. \ra{explain what's the consequence of
that} If we sample the gradient in a way that is not fully representative of
the dataset we might  experience one-time zero crossing which could wrongly
kill a neuron.

@@

\noindent\textbf{Preparing for Inference: } With ShrinkNets we obtain reduced-
sized networks during training, which is the first steps towards faster
inference. This networks are readily available for inference. However, because
they include switch layers---and therefore more parameters---they introduce
unnecessary overhead at inference time. To avoid this overhead, we reduce the
network parameters by combining each switch layer with its respective network
layer by multiplying the respective parameters before emitting the final
trained network.   \ra{can't we just simply prevent the following problem at
network design time?}In the unlikely case that a switch layer is sandwiched
between two non-linearly scalable layers, we leave the switch layer as is.

>>>>

\textbf{Sign change strategy}: Under this strategy neurons are removed when the
weight value changes its sign. This strategy works well in practice but it is
also sensitive to gradient noise. If we sample the gradient in a way that is
not fully representative of the dataset we might  experience one-time zero
crossing which could wrongly kill a neuron.

@@

\noindent\textbf{Preparing for Inference: } With ShrinkNets we obtain reduced-
sized networks during training, which is the first steps towards faster
inference. This networks are readily available for inference. However, because
they include switch layers---and therefore more parameters---they introduce
unnecessary overhead at inference time. To avoid this overhead, we reduce the
network parameters by combining each switch layer with its respective network
layer by multiplying the respective parameters before emitting the final
trained network. In the unlikely case that a switch layer is sandwiched
between two non-linearly scalable layers, we leave the switch layer as is.
